### 2020-06-29 Documents/ESA/sections/Intro.tex
Updated Literature Review and Introduction

    Swarm robotics bases its success upon the collaboration of many
    agents who contribute towards the overall goal of the system
    \cite{Hamann2018}. Such a collaboration can take the form of cooperative efforts or even
    competition, both resulting in behaviours that are far more complex thhan individual robots can
    achieve. The capacity for complexity is
    becoming increasingly important as robots are presented
    with ever more challenging tasks including: search and rescue,
    cleaning up space debris, and robotic assembly. Such tasks are
    beyond the capabilities of individual robots and so we must
    leverage the capacity for agents in a swarm to collectively
    achieve our goals. Fortunately, a growing subset of the Control
    Theory community has turned their attention towards this very
    problem and address the question: how does the dynamical behaviour
    of a population of agents change under the influence of control?
    Note that we use the term `agent' loosely here, an agent can refer
    to anything from a simple particle \cite{Roy2017} to a complex
    robot \cite{Elamvazhuthi2019}. In answering this question,
    researchers have gained a stronger understanding of how a swarm
    may be controlled to achieve desired results.

@@

    Importantly, the study will seek to understand the guarantees that can be
    placed on the safety of such systems in terms of their stability and
    constraint satisfaction. In doing so, we can ensure that a user can have
    confidence in the decision making and manipulation of the system.

>>>>

    Swarm robotics bases its success upon the collaboration of many
    agents who contribute towards the overall goal of the system
    \cite{Hamann2018}. Such a collaboration can take the form of cooperative efforts or even
    competition, both resulting in behaviours that are far more complex thhan individual robots can
    achieve. The capacity for complexity is
    becoming increasingly important as robots are presented
    with ever more challenging tasks including: search and rescue,
    cleaning up space debris, and robotic assembly. Such tasks are
    beyond the capabilities of individual robots and so we must
    leverage the capacity for agents in a swarm to collectively
    achieve our goals. Fortunately, a growing subset of the Control
    Theory community has turned their attention towards this very
    problem and address the question: how does the dynamical behaviour
    of a population of agents change under the influence of control?
    Note that we use the term `agent' loosely here, an agent can refer
    to anything from a simple particle \cite{Roy2017} to a complex
    robot \cite{Elamvazhuthi2019}. In answering this question,
    researchers have gained a stronger understanding of how a swarm
    may be controlled to achieve desired results and have shown its capabilites in a wide array of
    domains \cite{Sahin2005}.

@@

    Importantly, the study will seek to understand the guarantees that can be
    placed on the safety of such systems in terms of their stability and
    constraint satisfaction. If it is possible to determine, a priori, the decision making
    behaviour of a population through its learning dynamics in terms of known quantities (e.g. the
    agent parameters), then the system may be considered safe. Similarly, if it can be shown
    to be robust, and satisfy desired constraints (e.g. controls lying within desired limits), then
    we may be assured of its long-term safety. In doing so, we can ensure
    that a user can have confidence in the system's decision making and manipulation.

### 2020-06-29 Documents/ESA/sections/LitReview.tex
Updated Literature Review and Introduction

\textbf{TODO: Mention the parts of literature which we are not considering and explain why: Recent
MARL techniques (including MDRL), Marco Dorigo's work on Swarms. Add in the Learning in Stochastic
Games literature from Schwartz et al. Explain the concepts in Control Theory and how MPC works. Add
in suggestions for applications and papers supporting said applications.}

@@

Game theory can often be applied to problems of control theory
(particularly where there are multiple agents) to develop robust
controllers which guarantee properties of stability and constraint
satisfaction.

@@

Stochastic Games (or Markov Games) form a basis for MARL
settings. However, in this case the agents must learn about the
equilibrium strategies by playing the game, which means they do not
have a priori knowledge of the reward or transition functions. Schwarz \cite{SchwartzMulti-agentApproach}
considers two properties which should be used for evaluating MARL
algorithm: rationality and convergence. The latter simply states that
the method should converge to some equilibrium whereas the former
suggests that the method should learn the best response to stationary
opponents. A similar set of conditions is considered by Conitzer and
Sandholm in \cite{ConitzerAWESOME:}. Schwarz then presents a review of MARL methods (as of
September 2014).

@@

    \item {\em Robustness}: a system will perform its function in the presence of uncertainty and
    noise

    \item {\em Optimality}: the system will achieve some defined function

    \item {\em Feasibility}: the controller will always be able to generate a control law which
    satisfies the desired properties.
\end{itemize}

@@

@@

>>>>

@@

Game theory can often be applied to problems of control theory
(particularly where there are multiple agents) to develop robust
controllers which guarantee properties of stability and constraint
satisfaction. We define these in our review on Control Theory (see Section 
\ref{sec::Control_Theory}).

@@

Stochastic Games (or Markov Games) form a basis for MARL
settings. However, in this case the agents must learn about the
equilibrium strategies by playing the game, which means they do not
have a priori knowledge of the reward or transition functions. Schwarz \cite{SchwartzMulti-agentApproach}
considers two properties which should be used for evaluating MARL
algorithm: rationality and convergence. The latter simply states that
the method should converge to some equilibrium whereas the former
suggests that the method should learn the best response to stationary
opponents. A similar set of conditions is considered by Conitzer and
Sandholm in \cite{ConitzerAWESOME:}.

A plethora of MARL techniques emerged towards tackling this problem. Most notable of these are the
minimax Q-Learning algorithms proposed by Littman \cite{Littman} which focuses on zero-sum games and
Nash Q-Learning algorithm put forward by Hu and Wellman \cite{Hu} which extends the framework
towards general sum games. The details of such stochastic algorithms are beyond the scope of this
review as they consider multi-stage games (i.e. games in which the payoff matrix changes according
to state). Establishing the robustness of such systems is an ongoing area of research. However, as
of this review, it is not yet possible to place guarantees on the behaviour of MARL algorithms which
tackle multi-stage games. This is also true of more contemporary MARL algorithms, including that of
Multi-Agent Deep Reinforcement Learning (MDRL or MADRL), which are found to be incredibly sensitive
to changes in input \cite{Gleave}. Therefore, due to importance we place on the stability and
robustness guarantees of our MAS, we focus on those whose dynamics have been studies, as discussed
in the following section.

@@

    \item {\em Robustness}: a system will perform its function in the presence of uncertainty and
    noise.

    \item {\em Optimality}: the system will achieve its goal in the best way possible. This is
    determined using a loss function which the control laws must minimise.

    \item {\em Feasibility}: the controller will always be able to generate a control law which
    satisfies the desired properties. Many texts will refer to the well-posedness of the control
    problem which strictly requires that the control law: a) exist, b) be unique, c) vary
    continuously with initial conditions.
\end{itemize}

@@

\subsection{A Brief Introduction to Model Predictive Control} % (fold)
\label{sub:a_brief_introduction_to_model_predictive_control}

We begin by providing a brief introduction to the theory underlying model predictive control (MPC).
This begins with the theory of Optimal Control which, simply put, is the theoretical study of
controls which minimise a given cost function subject to system dynamics. More formally, an optimal
control problem is presented as

\begin{equation}
    \begin{split}
        \text{minimise } J(x, u) \\
        \text{s.t. }
        x(k + 1) = f(x(x_0; k, u(k)), u(k))\\
        u \in U_{ad},
    \end{split}
\end{equation}

where $J(x, u)$ is a given cost function, which is dependent on the state $x = x(x_0; k, u(k)) \in
X$ and control
$u(k)$, both of which are functions of the time step $k$. The first condition gives the dynamics of
system (i.e. how the state evolves in time given the controls). Here, we show the dynamical
system as an iterated map, though this may also be described through ordinary differential equations
(ODEs) or partial differential equations (PDEs). The second condition places constraints on the
controls $u$, which must lie within an admissible set. An example of this is bounded controls, in
which case the admissible set is given by

\begin{equation}
    U_{ad} := \{u \; | \; u_a(x) \leq u(x) \leq u_b(x) \; a.e. \; x \in X\}
\end{equation}

Our goal is to find the optimal control $\bar{u}$ which satisfies the condition

\begin{equation}
    J(\bar{x}, \bar{u}) \leq J(x, u) \; \forall u \in U_{ad}.
\end{equation}

The trouble with optimal controls is that they are open-loop, in that the controls are determined
for the model $x(k + 1) = f(x(k; x_0), u(k))$ a priori and simply applied to the system. Of course,
in the presence of noise, disturbances, or even errors in parameter estimation in the model itself,
such a control scheme is not practical.

The idea of MPC is to reduce the open-loop optimal control problem to a series of finite horizon
optimal control problems and solve these. For this reason, it is also referred to as `Receding
Horizon Control'. The control problem is, therefore, transformed to

\begin{equation}
    \begin{split}
        \text{minimise } J_N(x, u) := \sum_{k = 0}^{N-1} l(x(k), u(k)) \\
        \text{s.t. }
        x(k + 1) = f(x(k), u(k))\\
        u \in U_{ad},
    \end{split}
\end{equation}

where $l(x, u)$ are 'stage costs', defining the cost function at each time step of the horizon,
which is of length $N$. At each time step, the system updates its measurement of its state $x$ 
(which we have assumed here to be exact but may only be obtained through a measurement map). Solving
this yields the optimal control sequence for this horizon $\bar{u}(0), ... , \bar{u}(N-1)$ and the
first of these (i.e. $\bar{u}(0)$) is applied. Then, the system repeats this process at each time
step.

% subsection a_brief_introduction_to_model_predictive_control (end)

@@

Swarms are generally considered to be a special case of multi-agent systems and so, to this end,
Sahin \cite{Sahin2005} puts forward five qualities which must be satisfied for a system to be
considered a swarm. Note that Sahin's work considers swarm robotics, though these qualities apply to
any agent type (computational or biological).

\begin{enumerate}
    \item Autonomous agents: the agents can, independently, interact with the environment
    \item Large Number of Agents
    \item Few Homogenous groups of agents: Agents are considered homogenous if they follow similar
    rules and perform the same function.
    \item Relative incapability of the agent: The agents should not be able to carry out the task on
    their own, but rather efficient and robust handling of the task should emerge from the
    collaboration of the agents.
    \item Local sensing and communication: The agents should only have local sensing and
    communication capabilities.
\end{enumerate}
